---
title: "Melville Rotisserie Standings"
author: "Michael Fichman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(baseballr)
library(lubridate)
library(kableExtra)
library(purrr)
library(DT)

# Run source code to pull data from bbref, clean rosters and stats - will run to present day by calling Sys.Date()
# Rosters are hard coded in this file
source("~/GitHub/Melville_Rotisserie/R/clean_bbref.R")
```

# League Rules

- Teams accumulate stats from the beginning of the 2025 season until April 30th.

- Leading in a category is worth a point. Category leaders at season's end earn a point, most points wins!

- Teams consist of 8 position players, 1 Util/DH, 4 pitchers, and 4 bench players (C, IF, OF, P).

- No roster moves (trades, waivers, etc.,), except if a player *is placed on IR by their team*, in which case a bench player can be substituted (as OF, IF, or P) and their stats for the whole period used instead.

- Starting pitchers only.

# Current Standings

*Temporary data displaying 2024 batter and 2023-24 pitchers stats for drafted rosters - for testing purposes - includes playoffs*

*Data are pulled from Baseball Reference via baseballR on the date indicated in the page header*

```{r standings, echo = FALSE}
# Render Standings

left_join(stats_batting, stats_pitching, by = c("Owner" = "Owner")) %>%
  left_join(points_table, by = c("Owner" = "Owner")) %>%
  arrange(-Points) %>%
  mutate(across(where(is.numeric), ~ bold_stat(., cur_column()))) %>%
  select(Owner, Points, everything()) %>%
  kable(escape = FALSE) %>%
  kable_styling()

```

# Sortable Player Statistics



## Team Isaac

### Batters

```{r echo=FALSE}
# Roster display - Batters
datatable(batter_roster %>%
            filter(Owner == "Isaac") %>%
            select(positionBatters, Name, statusBatters, Owner, 
                   Team, G, PA, AB, R, 
                   H, HR, RBI, BB, SB, BA, 
                   OBP, SLG, OPS) %>%
            rename(Position = positionBatters,
                   Status = statusBatters), 
          options = list(pageLength = 12))

```


### Pitchers

```{r echo=FALSE}
datatable(pitcher_roster %>%
            filter(Owner == "Isaac") %>%
            select(positionPitchers, Name, statusPitchers, Owner, Team,
                   G, GS, W, L, IP, R, BB, SO, ERA, WHIP) %>%
            rename(Position = positionPitchers,
                   Status = statusPitchers), 
          options = list(pageLength = 10))

```

## Team Dad

### Batters

```{r echo=FALSE}
# Roster display - Batters
datatable(batter_roster %>%
            filter(Owner == "Dad") %>%
            select(positionBatters, Name, statusBatters, Owner, 
                   Team, G, PA, AB, R, 
                   H, HR, RBI, BB, SB, BA, 
                   OBP, SLG, OPS) %>%
            rename(Position = positionBatters,
                   Status = statusBatters), 
          options = list(pageLength = 12))

```


### Pitchers

```{r echo=FALSE}
datatable(pitcher_roster %>%
            filter(Owner == "Dad") %>%
            select(positionPitchers, Name, statusPitchers, Owner, Team,
                   G, GS, W, L, IP, R, BB, SO, ERA, WHIP) %>%
            rename(Position = positionPitchers,
                   Status = statusPitchers), 
          options = list(pageLength = 10))

```
