---
title: "Melville Rotisserie Standings"
author: "High Honorable League Commissioner Coach Mister Professor Michael"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(baseballr)
library(lubridate)
library(kableExtra)
library(purrr)
library(DT)

# Run source code to pull data from bbref, clean rosters and stats - will run to present day by calling Sys.Date()
# Initial date of league start needs to be hard coded
source("~/GitHub/Melville_Rotisserie/R/clean_bbref_multi.R")
```

# League Rules

**Current stats on the site are for demonstration only - with stats from beginning of the year, actual league play starts June 10th**

- Teams accumulate stats from June 10 to August 15.

- You get points based on your rank in each statistical category. If you are in first place in, for example, batting average - you get 5 points. If you are in second place - 3 points.Third place - 1 point. Fourth place - you get bupkis.

- Your lineup consists of:

  - 8 starting position players
  - 1 Util/DH player
  - 4 pitchers (starting pitchers only)
  - 4 bench players (C, IF, OF, P).


- No roster moves (trades etc.,), except if a player *is placed on IR by their team*, in which case a bench player can be substituted (as OF, IF, or P) and their stats for the whole period used instead. You aren't allowed to bring that player back - so if Bryce Harper gets hurt, and you replace him at 1B with reserve IF Pete Alonso from your bench... you can't bring Harper back later in the season - he's "flushed". You can replace Alonso on your bench with a free agent.

- All roster moves need to be communicated to High Honorable League Commissioner Coach Mister Professor Michael. Use email or text.

# Stats

How do we calculate the statistics we are using in the league?

## Batting Stats

-BA (Batting Average): Total Team Hits / Total Team At Bats

-HR: Total team home runs

-RBI: Total team runs batted in

-SB: Total team stolen bases

-OPS (On base pct plus slugging pct): (Hits + Walks / Plate Appearances) + (Total Bases / At bats)

## Pitching Stats

-IP: Total team innings pitched

-SO: Total team strikeouts

-ERA: Total earned runs per 9 innings

-WHIP: (Walks + Hits) / Innings Pitched

# News and Notes

The season starts June 15th. Expect the first update a few days afterwards.

# Current Standings

*Data are pulled from Baseball Reference via baseballR on the date indicated in the page header*

Bold-face numbers indicate the leader in each statistical category. 

```{r standings, echo = FALSE}
# Render Standings

left_join(stats_batting, stats_pitching, by = c("Owner" = "Owner")) %>%
  left_join(points_table, by = c("Owner" = "Owner")) %>%
  arrange(-Points) %>%
  mutate(across(where(is.numeric), ~ bold_stat(., cur_column()))) %>%
  select(Owner, Points, everything()) %>%
  kable(escape = FALSE) %>%
  kable_styling()

```

# Sortable Player Statistics

Sort through team and player statistics. You can type in your team's name in the search bar to look at only your team OR search for an individual player by name. This table only contains players drafted in the Melville Rotisserie league.

You can click on a statistic to sort the players from highest-to-lowest or lowest-to-highest.

## Batters


```{r echo=FALSE}
# Roster display - Batters
datatable(batter_roster %>%
            filter(batter_pitcher == "Batter") %>%
            select(Name, Position, Status, Owner, 
                   Team, G, AB, H, BB, HR, RBI, SB, BA, 
                  OPS), 
          options = list(pageLength = 12))

```


## Pitchers

```{r echo=FALSE}
datatable(pitcher_roster %>%
            select(Position, Name, Status, Owner, Team,
                   G, GS, W, L, IP, BB, SO, ERA, WHIP), 
          options = list(pageLength = 5))

```

