---
title: "Melville Rotisserie Standings"
author: "Michael Fichman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(baseballr)
library(lubridate)
library(kableExtra)
library(purrr)
library(DT)

# Run source code to pull data from bbref, clean rosters and stats - will run to present day by calling Sys.Date()
# Rosters are hard coded in this file
source("~/GitHub/Melville_Rotisserie/R/clean_bbref.R")
```

# League Rules

- Teams accumulate stats from the beginning of the 2025 season until April 30th.

- Leading in a category is worth a point. Category leaders at season's end earn a point, most points wins!

- Teams consist of 8 position players, 1 Util/DH, 4 pitchers, and 4 bench players (C, IF, OF, P).

- No roster moves (trades, waivers, etc.,), except if a player *is placed on IR by their team*, in which case a bench player can be substituted (as OF, IF, or P) and their stats for the whole period used instead.

- Starting pitchers only.

# News and Notes

These are the April League final standings.

Injury Report

Gerrit Cole (Michael) and Ronald Acuna (Isaac) were placed on Injured Reserve and were replaced in the lineup by bench players Tanner Houck and Fernando Tatis.

Each team can draft a new free agent player to refill their bench, but Cole and Acuna will be removed from their lineups.

# Current Standings

*Data are pulled from Baseball Reference via baseballR on the date indicated in the page header*

```{r standings, echo = FALSE}
# Render Standings

left_join(stats_batting, stats_pitching, by = c("Owner" = "Owner")) %>%
  left_join(points_table, by = c("Owner" = "Owner")) %>%
  arrange(-Points) %>%
  mutate(across(where(is.numeric), ~ bold_stat(., cur_column()))) %>%
  select(Owner, Points, everything()) %>%
  kable(escape = FALSE) %>%
  kable_styling()

```

# Sortable Player Statistics



## Team Isaac

### Batters

```{r echo=FALSE}
# Roster display - Batters
datatable(batter_roster %>%
            filter(Owner == "Isaac") %>%
            select(positionBatters, Name, statusBatters, Owner, 
                   Team, G, PA, AB, R, 
                   H, HR, RBI, BB, SB, BA, 
                   OBP, SLG, OPS) %>%
            rename(Position = positionBatters,
                   Status = statusBatters), 
          options = list(pageLength = 12))

```


### Pitchers

```{r echo=FALSE}
datatable(pitcher_roster %>%
            filter(Owner == "Isaac") %>%
            select(positionPitchers, Name, statusPitchers, Owner, Team,
                   G, GS, W, L, IP, R, ER, BB, SO, ERA, WHIP) %>%
            rename(Position = positionPitchers,
                   Status = statusPitchers), 
          options = list(pageLength = 10))

```

## Team Michael

### Batters

```{r echo=FALSE}
# Roster display - Batters
datatable(batter_roster %>%
            filter(Owner == "Michael") %>%
            select(positionBatters, Name, statusBatters, Owner, 
                   Team, G, PA, AB, R, 
                   H, HR, RBI, BB, SB, BA, 
                   OBP, SLG, OPS) %>%
            rename(Position = positionBatters,
                   Status = statusBatters), 
          options = list(pageLength = 12))

```


### Pitchers

```{r echo=FALSE}
datatable(pitcher_roster %>%
            filter(Owner == "Michael") %>%
            select(positionPitchers, Name, statusPitchers, Owner, Team,
                   G, GS, W, L, IP, R, ER, BB, SO, ERA, WHIP) %>%
            rename(Position = positionPitchers,
                   Status = statusPitchers), 
          options = list(pageLength = 10))

```
